Issues with Dynamical Measurements Across the Disk

### 2019-02-20 paper/ms.tex
Fix m12x macros

\newcommand{\unit}[2]{\ensuremath{\textrm{#1}^{\mathrm{#2}}}}
\newcommand{\m12i}{\textsf{m12i}}
\newcommand{\m12f}{\textsf{m12f}}
\newcommand{\m12m}{\textsf{m12m}}

@@

Cosmological simulations of Milky Way-mass galaxies are not perfect
representations of the true Milky Way in other ways as well, as discussed in
\citet{2018arXiv180610564S}. For instance, the velocity structure of m12i is
closer to M31's than the Milky Way's (Loebman et al. in prep). However, in
this work we are most interested in the global properties of the potential,
and specifically in deviations from axisymmetry. From this perspective, the
simulated galaxies are actually \emph{more} axisymmetric than we might expect
of the Milky Way. While they have prominent spiral arms, none has as strong a
bar as the MW does at present day, and none has a nearby companion like the
Large Magellanic Cloud. One of the three we consider (\m12f) does have an
ongoing interaction with a satellite galaxy similar to Sagittarius, which has
punched through the galactic disk outside the solar circle and induced some
warping. However, we expect that, as with the use of finite smoothing lengths,
the degree of midplane variation in the simulations is likely a factor of a
few lower than what could be expected in the MW.

>>>>

\newcommand{\unit}[2]{\ensuremath{\textrm{#1}^{\mathrm{#2}}}}

\newcommand{\mi}{\textsf{m12i}}
\newcommand{\mf}{\textsf{m12f}}
\newcommand{\mm}{\textsf{m12m}}

@@

Cosmological simulations of Milky Way-mass galaxies are not perfect
representations of the true Milky Way in other ways as well, as discussed in
\citet{2018arXiv180610564S}. For instance, the velocity structure of m12i is
closer to M31's than the Milky Way's (Loebman et al. in prep). However, in
this work we are most interested in the global properties of the potential,
and specifically in deviations from axisymmetry. From this perspective, the
simulated galaxies are actually \emph{more} axisymmetric than we might expect
of the Milky Way. While they have prominent spiral arms, none has as strong a
bar as the MW does at present day, and none has a nearby companion like the
Large Magellanic Cloud. One of the three we consider (\mf) does have an
ongoing interaction with a satellite galaxy similar to Sagittarius, which has
punched through the galactic disk outside the solar circle and induced some
warping. However, we expect that, as with the use of finite smoothing lengths,
the degree of midplane variation in the simulations is likely a factor of a
few lower than what could be expected in the MW.
